Weekday sleep, total cholestrol and the modifying effect of age on systolic blood pressure: An analysis of the 2015-2018 non-obese NHANES population

### 2023-12-11 manuscript/paper.Rmd
update

```{=html}
<!-- 
### Exposures:

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is,
\< 6 h, 6--8 h, ≥ 8 h respectively, and used \< 6 h as the reference
group in our analysis. We also explored the association between total
cholestrol (in mmol/L) level on systolic blood pressure including
potential effect modification by other factors.
-->
```
### Covariates:

```{=html}
<!-- Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is,
\< 6 h, 6--8 h, ≥ 8 h respectively, and used \< 6 h as the reference
group in our analysis. -->
```
Our analyses included the following as covariates: Race divided into
four groups as Mexican American, white, black and other race. Alcohol
consumption was grouped into drinking, no drinking, not recorded.
Smoking status as smoking, not smoking, not recorded. Diabetes was
defined as yes, no, borderline, or not recorded. Hypertension was
defined as yes, no, or not recorded. Snorting was defined as yes, no,
and not recorded. US citizenship status was defined as citizen by birth
or naturalization, don't know, not a citizen, or refused to answer.
Education level was grouped into four categories including graduate
studies, high school, less than grade 12 or some college. Additional
covariates included marital status, gender, age, albumin,
creatinine,hemoglobin, total cholesterol (TC), aspertate
aminotransferase (AST), high-density lipoprotein (HDL), and body mass
index (BMI). Details about these variables can be found at
<https://wwwn.cdc.gov/nchs/nhanes/search/default.aspx>. Age, albumin,
creatinine, hemoglobin, TC, AST, HDL, and BMI were analyzed as
continuous variables whereas gender, alcohol consumption, diabetes,
smoking, race, hypertension, and snorting were analyzed as categorical
variables. Sleep duration on workdays was also recorded and was
categorized into three groups, that is, \< 6 h, 6--8 h, ≥ 8 h
respectively, and used \< 6 h as the reference group in our analysis.
Table \@ref{tab:tabone} highlights the variable names and descriptions
as utilized in this study.

@@

@@

@@

## Subgroup analysis by gender

>>>>

### Exposures:

Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is,
\< 6 h, 6--8 h, ≥ 8 h respectively, and used \< 6 h as the reference
group in our analysis. We also explored the association between total
cholestrol (in mmol/L) level on systolic blood pressure including
potential effect modification by other factors.

### Covariates:

```{=html}
<!-- Sleep duration on workdays was evaluated by the questionnaire with the
following questions: "Number of hours usually sleep on weekdays or
workdays". We then categorized this variable into three groups, that is,
\< 6 h, 6--8 h, ≥ 8 h respectively, and used \< 6 h as the reference
group in our analysis. -->
```
Our analyses included the following as covariates: Race divided into
four groups as Mexican American, white, black and other race. Alcohol
consumption was grouped into drinking, no drinking, not recorded.
Smoking status as smoking, not smoking, not recorded. Diabetes was
defined as yes, no, borderline, or not recorded. Hypertension was
defined as yes, no, or not recorded. Snorting was defined as yes, no,
and not recorded. US citizenship status was defined as citizen by birth
or naturalization, don't know, not a citizen, or refused to answer.
Education level was grouped into four categories including graduate
studies, high school, less than grade 12 or some college. Additional
covariates included marital status, gender, age, albumin,
creatinine,hemoglobin, total cholesterol (TC), aspertate
aminotransferase (AST), high-density lipoprotein (HDL), and body mass
index (BMI). Details about these variables can be found at
<https://wwwn.cdc.gov/nchs/nhanes/search/default.aspx>. Age, albumin,
creatinine, hemoglobin, TC, AST, HDL, and BMI were analyzed as
continuous variables whereas gender, alcohol consumption, diabetes,
smoking, race, hypertension, and snorting were analyzed as categorical
variables. Table \@ref{tab:tabone} highlights the variable names and
descriptions as utilized in this study.

@@

### Variable selection based on univariate regression

Univariate regression analyses were performed on all potentially confounding covariates excluding hypertension. Model 1 was fitted to the data including the exposure variables as well as all potentially confounding covariates from univariate regression analysis. Model 2 was fitted to the same set of covariates including an interaction term between age and total cholesterol levels. Model 3 was fitted to the data including only covariates that had a statistically significant association with SBP in univariate analyses excluding HDL, hemoglobin, diabetes, survey cycle, and alcohol consumption. Model 4 included similar covariates as Model 3 but examined, in addition, all possible two-way interactions between the covariates. Model 5 included the same set of covariates as Model 3 in addition to an interaction term between age and total cholesterol levels.

### Variable selection based on LASSO and best subsets

@@

## Model performance evaluation

All models fitted to the data in this investigation were nested and evaluations were based on information criteria including Akaike Information Criteria (AIC) and Bayesian Information Criteria (BIC). [BIC] Additionally, we also used performance measures including the mean squared error (MSE), r-squared, and adjusted r-squared. The likelihood ratio test (LRT) was used in competing model comparisons testing the null hypothesis that the nested models are equivalent, and the extra parameters in the larger model do not improve the fit significantly, that is, these terms have effect sizes equivalent to 0. \@ref(tab:tabmodel) summarizes the model performance metrics compared for all models implemented in this investigation.

Here is where we add something....

## compare model 5 with model 2 because they have competing BIC and Adj R^2

@@

##
